---
title: "Data Science Fundamentals"
format: html
editor: visual
---

## What is a Data Scientist?

Data scientists are professionals that analyze data so that business/organizations can make better decisions. While closely related to statisticians, there are a few key differences between data scientists and statisticians. Namely,

-   data science is interdisciplinary
    -   data scientists use computer programming, statistics, and machine learning in their line of work; statisticians tend to be more focused and experts in a more narrow scope of work
-   statisticians *might* do some coding, whereas for data scientists coding is central!
    -   data scientists might also utilize software like Tableau to make nice visuals for their data because presentation is also crucial in their line of work; for statisticians this tends to not be as important

While I respect the rigorous nature of the statistician, I want to be a data scientist so ultimately I side with them!

## Code Example

Here is a simple example of work a data scientist might do. First, we define an object called y and list its class, internal type, and structure.

```{r}
y <- density(iris$Petal.Width)
class(y)
typeof(y)
str(y)
```

Next we plot y:

```{r}
plot(y, main = "Pedal Width Density Plot")
```
